Estimating Gaze Duration Error from Eye Tracking Data

### 2022-07-18 paper/paper.tex
Paper edits

The algorithm described in the preceding sections has been implemented as an open source python 
package called gazerr. It can be used as a software library, or deployed as a command line application. Source
code is available on GitHub () and the package can be installed from PyPi.

@@

We have demonstrated that the statistial information contained in eye tracking validation
data can be utilised for estimating errors in gaze duration estimation. The process involves
simulating the distribution of measurements for a given true durastion, and then inverting
it into a distribution over true duration for a given measurement.

We have released this approach as the open source application gazerr, and used it to explore
the relationship between fixation error and duration error. Our results show that the nature
of the error in gaze duration depends on the size of the measurement. Smaller measurements
tend toward over prediction, and larger measurements towards under prediction. We plotted
the relationship between expected error and saw that observed tendency toward smaller duration
measurements (estimated with an psuedo-exponential distribution) delivers a slower growing
expected duraiton error with the mean error in fixation points.

Finally, our simualtions revealed that for large error in fixation points certain measurements
become some unlikely that our monte carlo simualtions placed none of the probability density
in those regions. This strongly suggests that an additional downside to large fixation point error
is a reduced range of measurement for area of interest studies.

>>>>

The algorithm described in the preceding sections has been implemented as an open source python 
package called \textit{gazerr}. 
It can be used as a software library, exposing functions for calculating the probability densities,
or it can deployed as a command line application. 
The source code is available on GitHub and the python package can be installed from PyPi.

@@

We have demonstrated that the statistial information contained in eye tracking validation
data can be utilised for estimating errors in gaze duration estimation. The process involves
simulating the distribution of measured duration for each possible true duration, 
and then inverting it with Bayes rule into a distribution over true duration for a given measurement.

We have released this approach as the open source application \textit{gazerr} and used it to explore
the relationship between fixation error and duration error. Our results show that the nature
of the error in gaze duration depends on the size of the measurement. Smaller measurements
tend to have lower expected error while larger measurements tend toward under prediction. We plotted
the relationship between expected error and saw that observed tendency toward smaller duration
measurements (estimated with an psuedo-exponential distribution) delivers a slower growing
expected duration error with the mean error in fixation points.

Finally, our simualtions revealed that for large error in fixation points certain measurements
become so unlikely that our monte carlo simualtions placed none of the probability density
in those regions. This strongly suggests that an additional downside to large fixation point error
is a reduced range of measurement for area of interest studies.
